Appendix 2: Example of index standardization of fishery-independent survey data with sdmTMB

### 2022-03-17 doc/appendix-pcod-sdmTMB.Rmd
Add add_utm_columns()

We will fit a geostatistical spatiotemporal model with sdmTMB for the purposes of index standardization. We will use a data set built into the package: trawl survey data for Pacific Cod in Queen Charlotte Sound. The density units are kg/km^2^. Here, X and Y are UTM zone 9 coordinates in kilometres. 
If our spatial coordinates were not already in an equidistant projection, we would transform them [e.g., using `sf::st_transform()`, @pebesma2018] to ensure that distance remains constant throughout the study region.

>>>>

We will fit a geostatistical spatiotemporal model with sdmTMB for the purposes of index standardization. We will use a data set built into the package: trawl survey data for Pacific Cod in Queen Charlotte Sound. The density units are kg/km^2^. Here, X and Y are UTM zone 9 coordinates in kilometres. 
If our spatial coordinates were not already in an equidistant projection, we would transform them [e.g., using `sf::st_transform()`, @pebesma2018] to ensure that distance remains constant throughout the study region or using the built-in `sdmTMB::add_utm_columns()` function.
